\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
New test results

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 8.1 at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

@@

\subsubsection{Replacing the twins}
The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}. In line 2 the twins and falsetwins are defined and if there are none the program will terminate. If there are any twins all edges with a head or tail in one of these twins will be deleted. The complexity of this is $O(m +$ number of vertices (\emph{twins}+\emph{falsetwins}))$ < O (nm)$. Then in line 13-19 all vertices which are in twins or falsetwins will be removed. The complexity of this is $O(n^2)$. In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$). The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$). These twins also have much less than $n$ neighbours.

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec & 0.0056 sec \\
hugecographs & >30 min & 662.5381 sec & 0.0316 sec \\
cycles175 & 69.8579 sec & 70.8041 sec & 0.0215 sec\\
bigtrees3 & 8.2724 sec & 2.8264 sec & 0.0499 sec\\
cubes6 & 45.4422 sec & 45.4181 sec & 0.1503 sec\\
products72 & 7.5950 sec & 7.5198 sec & 0.0275 sec\\
torus72 & 25.4586 sec & 25.5244 sec & 0.0167 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}

>>>>

\subsection{Experiment Setup}
For the testing, a single laptop was used to collect all the timed data. The tests were run in JetBrains' PyCharm, using the built-in functions to run the python code. The python interpreter used was Python 3.4 and the laptop was running Windows 10 Pro Technical Preview (at 3.5 GHz and 8.00 GB) at the time of the testing. Efforts were made to ensure all the testing was performed under the same circumstances.

@@

\subsubsection{Replacing the twins}
The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}. In line 2 the twins and falsetwins are defined and if there are none the program will terminate. If there are any twins all edges with a head or tail in one of these twins will be deleted. The complexity of this is $O(m +$ number of vertices in (\emph{twins}+\emph{falsetwins}))$ < O (nm)$. Then in line 13-19 all vertices which are in twins or falsetwins will be removed. The complexity of this is $O(n^2)$. In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$). The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$). These twins also have much less than $n$ neighbours.

@@

\section{Table with computation times}
\begin{table}[h]
\begin{tabular}{c|C{0.3\textwidth}|C{0.3\textwidth}|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) & Preprocessing time \\
\hline
cographs1 & 6.6017 sec & 0.0048 sec & 0.0027 sec \\
hugecographs & >30 min & 29.8713 sec & 0.0214 sec \\
cycles175 & 13.7522 sec & 13.9265 sec & 0.0238 sec\\
bigtrees3 & 0.9652 sec & 0.2700 sec & 0.0323 sec\\
cubes6 & 0.5967 sec & 0.5877 sec & 0.0072 sec\\
products72 & 0.6083 sec & 0.6353 sec & 0.0123 sec\\
torus72 & 3.5590 sec & 3.6059 sec & 0.0106 sec\\
\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}

\section{Complexity}
\begin{table}[h]
\begin{tabular}{c|c}
n & time \\
\hline
34 & 0.0017\\
66 & 0.0032\\
130 & 0.0071\\
258 & 0.161\\
514 & 0.0344\\
1026 & 0.0805\\
2050 & 0.2019\\
4098 & 0.5874\\
8194 & 2.7102

\end{tabular}
\caption{Table showing the result from the experiment. For each set of graphs, it shows the computation time without and with preprocessing time, as well as the time it took to perform the preprocessing.}
\label{table:results}
\end{table}
\end{appendices}
